Structured Versus Decorated Cospans

### 2022-03-21 ResponseToReviews.tex

I think it would be worth saying in words a bit more prominently what the hypothesis of theorem 4.1 roughly means, namely that the fibers of the total 
category have finite colimits, reindexing preserves them, and the monoidal product on the fibers is cocartesian.

I wonder if the “problem” where DCsp is not a structured cospan category could be “fixed” by upgrading the functor from Set to Cat in a non-discrete 
way, for example with an ordering with the zero vector field as the bottom element. I suppose this would give you different 2-cells in the resulting 
double category or bicategory, but perhaps it would yield the same 1-category}

\section{Our Answer}
\fi

We have changed the paper in response to the four referees' comments.  We list those comments below, along with our responses which are in boldface.

\section*{First Review}

@@

{\bf Done.}

\item COVID paragraph: I appreciate the effort into explaining the applied aspect. However, claims about the software (it is ``easy'', we ``easily'' modify, we ``better understand'') sound too vague (is it computationally better? do we assume that the final user understands structured cospans? are we comparing  it to other Petri net editors?). Perhaps this paragraph could be fused as a comment to the previous one, which is already a very good justification  for the use of Petri nets with rates.

{\bf There is now a paper by detailing how this software works, so according to this suggestion we have changed our paper so that it  refers to that other paper, along with the AlgebraicPetri GitHub repository which contains the code.}

\iffalse
  {\john But we still need to add an arXiv link in reference 1!  It should be on the arXiv soon.}

@@

{\kenny Can we put ``In preparation." if they don't have this on the arXiv in a timely manner?}

{\chris Sounds good to me...}

{\john Yes, we can do that.  Their paper is written, but they are struggling to get it onto the arXiv... and having trouble for stupid technical reasons.   I'll see if they succeed by the time we submit this.}

{\chris Great! The 
%hyperref link ??? opens up notes by Kenny for me, I don't know how or why.}

{\john It's weird that the line ??? opens up anything for you.  It'll go away when we get the arXiv number.} Indeed!
\fi

### 2022-03-21 cospans_new.tex
added sentence to end of conclusion
a couple of small things

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor $\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.   Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, we know ${}_L\lCsp(\widehat{D})$ cannot be a decorated cospan double category.  A simple example where $R$ is not an opfibration was provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.

>>>>

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
$\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf 
categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
${}_L\lCsp(\widehat{D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
show that ${}_L\lCsp(\widehat{D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
guarantee ${}_L\lCsp(\widehat{D})$ is isomorphic to a decorated cospan category, using the above machinery.
